Hybrid platforms and bargaining

### 2023-04-19 src/presentation/topics_talk.qmd
Add manim figure for equilibrium entry

::: {.fragment fragment-index=1}
 - Hybrid mode reduces fringe entry
$$
\small
\frac{\partial N_F^*}{\partial N_P} < 0
$$
:::
::: {.fragment fragment-index=2}
 - And, under certain conditions, total profits: if $\small f(N_P, N_F) = g(\alpha N_P + \beta N_F)$, $w(s) \equiv 1$ and $g'' < 0$
$$
\small\text{Then } \frac{\partial N_F^*}{\partial N_P} < -\frac{\alpha}{\beta}
$$
:::

@@

::: {.fragment fragment-index=1}

:::
::: {.fragment fragment-index=2}

@@

## Production
::: {.fragment}
 - Assume that the platform prices its products as if they were made by seperate, competitive sellers
   - Possible interpretation: profit-maximizing subsidiaries
   - More importantly: provides a nice benchmark
:::
::: {.fragment}
 - The optimal price is an additive markup rule:
 $$
 \begin{align*}
 p^*_{Ti} &= c_T + \mu \\
 \pi^{v*}_{Ti} &= \mu \frac{\exp \left( \frac{v_T - c_T - \mu}{\mu} \right)}{A}
 \end{align*}
 $$
:::
::: {.fragment}
 - The optimal price is an additive markup rule:
 $$
 \begin{align*}
 p^*_{Ti} &= c_T + \mu \\
 \pi^{v*}_{Ti} &= \mu \frac{\exp \left( \frac{v_T - c_T - \mu}{\mu} \right)}{A}
 \end{align*}
 $$
:::

>>>>

::: {.fragment fragment-index=3}
 - If $\frac{\partial^2 f(N_P, n_F)}{\partial n_P \partial n_F} < 0$, hybrid mode reduces fringe entry

:::
::: {.fragment fragment-index=4}
 - And sometimes total profits, too
 $$
 \begin{gather*}
   g(\alpha N_P + \beta N_F), \\
   g'' < 0, w(s) \equiv 1
 \end{gather*}
 $$
 $$
 \implies \frac{\partial N_F^*}{\partial N_P} < -\frac{\alpha}{\beta}
 $$
:::

@@

::: {.fragment fragment-index=1}
  <video data-autoplay src="../../out/manim_figures/videos/comparative_equilibrium_entry/800p60/sections/draw_graph.mp4" />
:::
::: {.fragment fragment-index=2}
  <video data-autoplay src="../../out/manim_figures/videos/comparative_equilibrium_entry/800p60/sections/mark_equilibrium.mp4" />
:::
::: {.fragment fragment-index=3}
  <video data-autoplay src="../../out/manim_figures/videos/comparative_equilibrium_entry/800p60/sections/alternate_equilibrium.mp4" />
:::
::: {.fragment fragment-index=4}
  <video data-autoplay src="../../out/manim_figures/videos/comparative_equilibrium_entry/800p60/sections/show_loss.mp4" />
:::

@@

## Production
::: {.fragment}
 - Assume that the platform prices its products as if they were made by seperate, competitive sellers
   - Possible interpretation: profit-maximizing subsidiaries
   - More importantly: provides a nice benchmark
:::
::: {.fragment}
 - The optimal price is an additive markup rule:
 $$
 \begin{align*}
 p^*_{Ti} &= c_T + \mu \\
 \pi^{v*}_{Ti} &= \mu \frac{\exp \left( \frac{v_T - c_T - \mu}{\mu} \right)}{A}
 \end{align*}
 $$
:::
